A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface\tnoteref{t1}

### 2022-03-04 sections/model_overview/main.tex
Minor changes
- Minor changes to sections and subsections
- Move figure from game section to queueing section

\begin{figure}[ht]
    \centering
    \begin{tikzpicture}[>=stealth, scale=0.8],
        % the rectangle of Queue 1
        \draw (0,0) -- ++(3cm,0) -- ++(0,-1.5cm) -- ++(-3cm,0);
        % The label above Queue 1 -> M
        \node[anchor=north] at (1.5cm, 1cm) {\( 
            \overbrace{\qquad \qquad \qquad \qquad}^{M} 
        \)};
        % The label below Queue 1 -> Parking space
        \node[anchor=north] at (1.5cm, -1.7cm) {\small{Parking space}};

        % the vertical lines in Queue 1
        \foreach \i in {1,...,5, 6.6}
        \draw (3cm-\i*13pt,0) -- +(0,-1.5cm);

        % % the circle in Queue 1
        % \draw (2.75,-0.75cm) circle [radius=0.75cm] node {\(0\)};

        % the rectangle in Queue 2
        \draw (5,1.25) -- ++(2cm,0) -- ++(0,-1.5cm) -- ++(-2cm,0);
        % the vertical lines in Queue 2
        \foreach \i in {1,...,4, 5.7}
        \draw (7cm-\i*10pt,1.25) -- +(0,-1.5cm);
        % The two vertical lines at the start of Queue 2 
        \draw (7cm-54pt,1.2) -- +(0,-0.5cm);
        \draw (7cm-54pt,0.3) -- +(0,-0.5cm);        
        \draw (7cm-51pt,1.1) -- +(0,-0.4cm);
        \draw (7cm-51pt,0.3) -- +(0,-0.4cm);

        % The label between the lines for T
        \node[anchor=north] at (5.15, 0.80 cm) {\small{\( T \)}};

        % The label above Queue 2 -> N
        \node[anchor=north] at (6.6cm, 2.2cm) {\( 
            \overbrace{\qquad \qquad \qquad \qquad}^{N} 
        \)};
        % The label below Queue 2 -> Hospital
        \node[anchor=north] at (6.2cm, -0.5cm) {\small{Hospital}};

        % the circle in Queue 2
        \draw (7.75,0.5) circle [radius=0.75cm] node {\(C\)};

        % Arrow line from Queue 2 outside
        \draw[->] (8.5,0.525) -- +(20pt,0);

        % Line from lambda_2 to Queue 1
        \draw[<-] (-0.3,-0.75) -- +(-40pt,0) node[left] {\( \lambda_2 \)};
        % First line (horizontal) after Queue 1
        \draw[-] (3,-0.75) -- +(34pt,0);
        % Second line (vertical) after Queue 1
        \draw (4.2, 0.525) -- (4.2, -0.75);

        % First line (horizontal) from lambda_1
        \draw (4.2, 1.8) -- +(-169.5pt,0) node[left] {\( \lambda_1 \)};
        % Second line (vertical) from lambda_1
        \draw (4.2, 1.8) -- (4.2, 0.525);
        % Arrow line to Queue 2
        \draw[->] (4.2, 0.525) -- (4.8, 0.525);  
    \end{tikzpicture}
    \caption{A diagrammatic representation of the queueing model. 
    The threshold \(T\) only applies to type 2 individuals.
    If the number of individuals in the hospital is \(T\), only 
    individuals of type 1 
    are accepted (at a rate \(\lambda_1\)) and individuals of type 2
    (arriving at a rate \(\lambda_2\)) are blocked in the parking space.}
    \label{fig:diagram_of_queueing_system}
\end{figure}

>>>>

% TODO: Add figure here of the game as described by issue #32

### 2022-03-04 sections/queueing_model/main.tex
Minor changes
- Minor changes to sections and subsections
- Move figure from game section to queueing section

>>>>

\begin{figure}[ht]
    \centering
    \begin{tikzpicture}[>=stealth, scale=0.8],
        % the rectangle of Queue 1
        \draw (0,0) -- ++(3cm,0) -- ++(0,-1.5cm) -- ++(-3cm,0);
        % The label above Queue 1 -> M
        \node[anchor=north] at (1.5cm, 1cm) {\( 
            \overbrace{\qquad \qquad \qquad \qquad}^{M} 
        \)};
        % The label below Queue 1 -> Parking space
        \node[anchor=north] at (1.5cm, -1.7cm) {\small{Parking space}};

        % the vertical lines in Queue 1
        \foreach \i in {1,...,5, 6.6}
        \draw (3cm-\i*13pt,0) -- +(0,-1.5cm);

        % % the circle in Queue 1
        % \draw (2.75,-0.75cm) circle [radius=0.75cm] node {\(0\)};

        % the rectangle in Queue 2
        \draw (5,1.25) -- ++(2cm,0) -- ++(0,-1.5cm) -- ++(-2cm,0);
        % the vertical lines in Queue 2
        \foreach \i in {1,...,4, 5.7}
        \draw (7cm-\i*10pt,1.25) -- +(0,-1.5cm);
        % The two vertical lines at the start of Queue 2 
        \draw (7cm-54pt,1.2) -- +(0,-0.5cm);
        \draw (7cm-54pt,0.3) -- +(0,-0.5cm);        
        \draw (7cm-51pt,1.1) -- +(0,-0.4cm);
        \draw (7cm-51pt,0.3) -- +(0,-0.4cm);

        % The label between the lines for T
        \node[anchor=north] at (5.15, 0.80 cm) {\small{\( T \)}};

        % The label above Queue 2 -> N
        \node[anchor=north] at (6.6cm, 2.2cm) {\( 
            \overbrace{\qquad \qquad \qquad \qquad}^{N} 
        \)};
        % The label below Queue 2 -> Hospital
        \node[anchor=north] at (6.2cm, -0.5cm) {\small{Hospital}};

        % the circle in Queue 2
        \draw (7.75,0.5) circle [radius=0.75cm] node {\(C\)};

        % Arrow line from Queue 2 outside
        \draw[->] (8.5,0.525) -- +(20pt,0);

        % Line from lambda_2 to Queue 1
        \draw[<-] (-0.3,-0.75) -- +(-40pt,0) node[left] {\( \lambda_2 \)};
        % First line (horizontal) after Queue 1
        \draw[-] (3,-0.75) -- +(34pt,0);
        % Second line (vertical) after Queue 1
        \draw (4.2, 0.525) -- (4.2, -0.75);

        % First line (horizontal) from lambda_1
        \draw (4.2, 1.8) -- +(-169.5pt,0) node[left] {\( \lambda_1 \)};
        % Second line (vertical) from lambda_1
        \draw (4.2, 1.8) -- (4.2, 0.525);
        % Arrow line to Queue 2
        \draw[->] (4.2, 0.525) -- (4.8, 0.525);  
    \end{tikzpicture}
    \caption{A diagrammatic representation of the queueing model. 
    The threshold \(T\) only applies to type 2 individuals.
    If the number of individuals in the hospital is \(T\), only 
    individuals of type 1 
    are accepted (at a rate \(\lambda_1\)) and individuals of type 2
    (arriving at a rate \(\lambda_2\)) are blocked in the parking space.}
    \label{fig:diagram_of_queueing_system}
\end{figure}
